### 2016-11-22 docs/ms_communitySynchrony.tex
slight changes for Ecology submission
final small edits for R1 submission

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}
\usepackage{times}
\usepackage[document]{ragged2e}

@@

\begin{abstract}
Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

@@

\subsection{INTRODUCTION}\label{introduction}

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding in different ways to environmental fluctuations
(environmental stochasticity), or fluctuating asynchronously because of
random chance events (demographic stochasticity) (Isbell et al. 2009,
Hector et al. 2010, {{de Mazancourt}} et al. 2013). Species richness
affects synchrony because larger species pools are more likely to
contain species that respond disimilarly to environmental conditions
(Yachi and Loreau 1999), implying that species losses will reduce
ecosystem stability. Even without species losses, abiotic homogenization
can weaken compensatory dynamics and, in turn, decrease temporal
stability of ecosystem functioning (Hautier et al. 2014). The link
between synchrony and stability means that a mechanistic understanding
of synchrony can help us predict the impacts of global change on
ecosystem stability.

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
interspecific interactions (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009). For example, in a community composed of large
populations (no demographic stochasticity) with weak interspecific
interations, community-wide species synchrony should be determined by
the covariance of species' responses to the environment (Loreau and {{de
Mazancourt}} 2008). However, this prediction relies on a relatively
simple population model and only holds under two assumptions: (i)
species' responses to the environment are similar in magnitude and (ii)
all species have similar growth rates. Whether such theoretical
predictions hold in natural communities where species differences are
unlikely to be symmetrical is unkown because few studies have explicitly
tested theory on the drivers of species synchrony in natural communities
(Mutshinda et al. 2009, Thibaut et al. 2012), and they did not consider
demographic stochasiticity.

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from the covariance matrix of species
abundances (e.g., Houlahan et al. 2007) is impossible. This is because
an unbiased null expectation for synchrony does not exist (Loreau and
{{de Mazancourt}} 2008) and observed synchrony can arise from non-unique
combinations of factors (Ranta et al. 2008). For example, weak synchrony
of population abundances could reflect positive environmental
correlations (synchronizing effect) offset by strong competition
(desynchronizing effect), or negative environmental correlations and
weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific interactions is to remove
them one-by-one, and in combination. In principle, this could be done in
an extremely controlled laboratory setting, but empirically-based models
of interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that positively correlated environmental responses among species
determined community dynamics. Thibaut et al. (2012) used a similar
approach for reef fish and came to a similar conclusion: environmental
responses determine synchrony. While a major step forward, Mutshinda et
al.'s (2009) and Thibaut et al.'s (2012) modeling technique relied on
abundance data that may or may not reliably capture competitive
interactions that occur at the individual level. Furthermore, although
both studies quantified the relative importance of environmental
stochasticity and interspecific interactions to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific interactions on species synchrony in
natural plant communities. To achieve these objectives, we first refine
theory that has been used to predict the effects of species richness on
ecosystem stability ({{de Mazancourt}} et al. 2013) and species
synchrony (Loreau and {{de Mazancourt}} 2008) to generate predictions of
community-wide species synchrony under two limiting cases derived from
the dynamics of individual species in monoculture. We then confront our
theoretical predictions with simulations from the empirically-based
population models. Second, we use the multi-species population models to
perform simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific interactions
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

\subsection{THEORETICAL MODEL}\label{theoretical-model}

\subsubsection{The model}\label{the-model}

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}`s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Appendix S1). Due to the linear
approximation approach, our analytical predictions will likely fail in
communities where species exhibit large fluctuations due to limit cycles
and chaos (Loreau and {{de Mazancourt}} 2008). Indeed, one of the
advantages of focusing on growth rates rather than abundances is that
growth rates are more likely to be well-regulated around an equilibrium
value, if the long-term average of a species' growth rate is relatively
small (e.g., \(r < 2\)).

\subsubsection{Predictions}\label{predictions}

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}. Confronting our theoretical predictions with data
requires estimates of species dynamics of large populations (no
demographic stochasticity) growing in isolation (no interspecific
interactions) to calculate the covariance of species' environmental
responses. To estimate environmental responses in natural communities,
we turn to our population models built using long-term demographic data.

\subsection{EMPIRICAL ANALYSIS}\label{empirical-analysis}

\subsubsection{Materials and methods}\label{materials-and-methods}

\paragraph{Data}\label{data}

@@

\paragraph{Calculating observed
synchrony}\label{calculating-observed-synchrony}

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal variance of species
\emph{i'}s per capita population growth rate (\(r_i\)) and
\(\sigma^{2}_{T}\) is the temporal variance of the aggregate
community-level growth rate. \(\phi\) ranges from 0 at perfect
asynchrony to 1 at perfect synchrony (Loreau and {{de Mazancourt}}
2008). We use the same equation to calculate observed synchrony of
species' percent cover, which we present to relate our results to
previous findings, even though we focus on synchrony of growth rates in
our model simulations (see below).

\paragraph{Fitting statistical models}\label{fitting-statistical-models}

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Crowding was treated as a fixed effect without a temporal
component because most 95\% credible intervals for random year effects
on crowding broadly overlapped zero and, in a test case, including
yearly crowding effects did not change our results. Spatial (quadrat
groupings) variation was treated as a random effect on the intercept and
temporal (interannual) variation was treated as random effects on the
intercept and the effect of genet size in the previous year (Appendix
S1).

@@

\paragraph{Building dynamic multi-species
models}\label{building-dynamic-multi-species-models}

Once we have fit the vital rate statistical models, building the
population models is straightforward. For the IBM, we initialize the
model by randomly assigning plants spatial coordinates, sizes, and
species identities until each species achieves a density representative
of that observed in the data. We then project the model forward by using
the survival regression to determine whether a genet lives or dies, the
growth regression to calculate changes in genet size, and the
recruitment regression to add new individuals that are distributed
randomly in space. Crowding is directly calculated at each time step
since each genet is spatially referenced (as in the observed data).
Environmental stochasticity is not an inherent feature of IBMs, but is
easily included since we fit year-specific temporal random effects for
each vital rate regression. To include temporal environmental variation,
at each time step we randomly choose a set of estimated survival,
growth, and recruitment parameters specific to one observation year. For
all simulations, we ignore the spatial random effect associated with
variation among quadrat groups, so our simulations represent an average
quadrat for each site.

The IPM uses the same vital rate regressions as the IBM (Rees and Ellner
2009, Rees et al. 2014), but it is spatially implicit and does not
include demographic stochasticity. Following Chu and Adler (2015), we
use a mean field approximation that captures the essential features of
spatial patterning to define the crowding index at each time step
(Supporting Online Information). Temporal variation is included in
exactly the same way as for the IBM. For full details on the IPMs we
use, see Chu and Adler (2015).

\paragraph{Simulation experiments}\label{simulation-experiments}

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific interactions)
were removed one-by-one and in combination. To remove interspecific
interactions, we set the off-diagonals of the interaction matrix for
each vital rate regression to zero. This retains intraspecific
interactions, and thus density-dependence, and results in simulations
where species are growing in isolation. We cannot definitively rule out
the effects of species interactions on all parameters, meaning that a
true monoculture could behave differently than our simulations of a
population growing without interspecific competitors. To remove the
effect of a fluctuating environment, we removed the temporal
(interannual) random effects from the regression equations. To remove
the effect of demographic stochasticity, we use the IPM rather than the
IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Indeed, results from an IBM with infinite population
size would converge on results from the IPM. Given computational
constraints, the largest landscape we simulate is a 25 \(\text{m}^2\)
plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
interspecific interactions) present; (2) IPM: Demographic stochasticity
removed; (3) IBM: Environmental stochasticity removed; (4) IBM:
Interspecific interactions removed; (5) IPM: Interspecific interactions
and demographic stochasticity removed; (6) IBM: Interspecific
interactions and environmental stochasticity removed. We ran IPM
simulations for 2,000 time steps, after an initial 500 iteration burn-in
period. This allowed species time to reach their stable size
distribution. We then calculated the synchrony of species' per capita
growth rates over 100 randomly selected contiguous 50 time-step
sections. We ran IBM simulations for 100 time steps, and repeated the
simulations 100 times for each simulation experiment. From those, we
retained only the simulations in which no species went extinct due to
demographic stochasticity. Synchrony was calculated over the 100 time
steps for each no extinction run within a model experiment. To explore
the effect of demographic stochasticity in different sized populations,
we ran simulations (1) and (6) on plot sizes of 1, 4, 9, 16, and 25
\(\text{m}^2\). All other IBM simulations were run on a 25
\(\text{m}^2\) landscape.

Results from our simulation experiments also allow us to test our
theoretical predictions. First, in the absence of interspecific
interactions and demographic stochasticity, populations can only
fluctuate in response to the environment. Therefore, we can use results
from simulation (5) to estimate the covariance of species' responses to
the environment (\(\text{cov}(u_{ie}, u_{je})\)) and parameterize
Equation 4. Parameterizing Equation 3 does not require simulation output
because the only parameters are the species' relative abundances.
Second, simulations (5) and (6) represent the simulated version of our
limiting case theoretical predictions. Thus, we directly test the
theoretical predictions by comparing them to observed synchrony and
simulated synchrony.

\subsubsection{Results}\label{results}

Synchrony of species' per capita growth rates at our study sites range
from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to
0.92 (Table 2). Synchrony tends to be higher in communities with few
species (Arizona and New Mexico) and/or with relatively high temporal
variability in percent cover (e.g., Montana). Synchrony is lowest in
Idaho, the only data set that includes two life forms: a shrub and three
perennial grasses (Table 1). Synchrony of per capita growth rates and CV
of percent cover are positively correlated (Pearson's \(\rho\) = 0.72).
For all five communities, species synchrony from IPM and IBM simulations
closely approximated observed synchrony (Fig. S1). IBM-simulated
synchrony is consistently, but only slightly, lower than IPM-simulated
synchrony (Fig. S1), likely due to the desynchronizing effect of
demographic stochasticity.

>>>>

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}
\usepackage{times}
\usepackage[document]{ragged2e}
\usepackage{titlesec}
\titleformat{\section}{\normalsize\sc\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\it\centering}{\thesubsection}{1em}{}
\titleformat*{\paragraph}{\normalsize\it}

@@

\begin{abstract}
Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative \textcolor{blue}{influence} of these factors \textcolor{blue}{on the synchrony of dominant species in five semiarid grasslands.}
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. 
\textcolor{blue}{For the dominant species in these plant communities}, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

@@

\section{Introduction}

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010).
\textcolor{blue}{The stabilizing effect of species richness arises from a combination of selection effects and complementarity}
(Loreau and Hector 2001).
\textcolor{blue}{Selection effects occur when a dominant species has lower than average temporal variability, which generates a positive effect on ecosystem stability}
(e.g., Grman et al. 2010).
\textcolor{blue}{Complementarity occurs when species have unique temporal dynamics, causing their abundances to fluctuate asynchronously, increasing ecosystem stability.}
\textcolor{blue}{The premise of this paper is that understanding the mechanisms driving species' temporal dynamics, and resulting (a)synchrony, is necessary to predict the impacts of global change on ecosystem stability.}

\textcolor{blue}{Asynchronous dynamics, also known as compensatory dynamics}
(Gonzalez and Loreau 2009),
\textcolor{blue}{occur whenever species synchrony is not perfect} and
result from individual species responding in different ways to
environmental fluctuations, random chance events, and/or competitive
interactions (Isbell et al. 2009, Hector et al. 2010, {{de Mazancourt}}
et al. 2013, Gross et al. 2014). Species richness affects
\textcolor{blue}{the degree of synchrony in a community} because larger
species pools are more likely to contain species that respond
dissimilarly to environmental conditions, reducing synchrony and
increasing stability (Yachi and Loreau 1999).
\textcolor{blue}{Species richness can also affect synchrony if the strength of species interactions varies systematically with richness, because competition generally increases synchrony and reduces stability}
(Loreau and {{de Mazancourt}} 2013, but see Gross et al. 2014).

\textcolor{blue}{The effects of environmental change and species losses on ecosystem stability will depend on whether synchrony is driven by species-specific responses to environmental conditions or interspecific competition}
(Hautier et al. 2014).
\textcolor{blue}{If responses to environment are important, then environmental change could alter synchrony and stability.
If competition is important, then the direct effects of environmental change may not affect synchrony and stability, but species gains/losses will.}

\textcolor{blue}{The relative role of environmental responses and competition in driving synchrony  in natural plant communities}
remains controversial (reviewed in Gonzalez and Loreau 2009). One source
of the controversy is that quantifying the relative strengths of each
driver based on the covariance matrix of species abundances (e.g.,
Houlahan et al. 2007) is impossible. This is because observed synchrony
can arise from non-unique combinations of factors (Ranta et al. 2008).
For example, weak synchrony of population abundances could reflect
positive environmental correlations (synchronizing effect) offset by
strong competition (desynchronizing effect), or negative environmental
correlations and weak competition.

\textcolor{blue}{Theory can help us resolve this empirical question.}
Recent theoretical work has identified three determinants of species
synchrony: environmental stochasticity, interspecific interactions, and
demographic stochasticity (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009).
\textcolor{blue}{This theory has been developed by focusing on simple limiting cases in which only one of these three drivers operates.}
For example, in a community composed of large populations (no
demographic stochasticity) with weak interspecific interations,
community-wide species synchrony should be determined by the covariance
of species' responses to the environment (Loreau and {{de Mazancourt}}
2008). However, this prediction relies on a relatively simple population
model and \textcolor{blue}{depends on two restrictive} assumptions: (i)
species' responses to the environment are similar in magnitude and (ii)
all species have similar growth rates. Whether such theoretical
predictions hold in natural communities where species differences are
unlikely to be symmetrical is unkown because few studies have explicitly
tested theory on the drivers of species synchrony in natural communities
(Mutshinda et al. 2009, Thibaut et al. 2012), and they did not consider
demographic stochasiticity.

An intuitive way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific interactions is to remove
them one-by-one, and in combination.
\textcolor{blue}{If synchrony changes more when we remove environmental stochasticity than when we remove interspecific interactions, we would conclude that environmental fluctuations are the more important driver.}
In principle, this could be done in an extremely controlled laboratory
setting (e.g., Venail et al. 2013), but empirically-based models of
interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that positively correlated environmental responses among species
determined community dynamics. Thibaut et al. (2012) used a similar
approach for reef fish and came to a similar conclusion: environmental
responses determine synchrony.

While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique does have some limitations.
\textcolor{blue}{First, although both studies quantified the relative importance of environmental stochasticity and interspecific interactions to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony would change if each factor were removed.
Second, they relied on popluation abundance data that may or may not reliably capture competitive interactions occuring at the individual level.
Third, fluctuations in abundance may mask the mechanisms that underpin species synchrony.
The synchrony of species' abundances ultimately determines the stability of total community biomass, but the processes that drive species synchrony are most tightly linked to each species' immediate response to environmental conditions and competition}
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Therefore, we focus on per capita growth rates, which represent a species' immediate response to interannual fluctuations.}

Here, we use multispecies population models fit to long-term demographic
data from five semi-arid plant communities to test theory on the drivers
of species synchrony (Fig. 1). Our objectives are to (1) derive and test
theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, interspecific
interactions, and demographic stochasticity on
\textcolor{blue}{the synchrony of dominant species} in natural plant
communities.
\textcolor{blue}{While our focus is limited to dominant species due to data constraints, previous work indicates that the dynamics of dominant species determine ecosystem functioning in grasslands}
(Smith and Knapp 2003, Bai et al. 2004, Grman et al. 2010, Sasaki and
Lauenroth 2011).

To achieve our objectives, we first refine theory that has been used to
predict the effects of species richness on ecosystem stability ({{de
Mazancourt}} et al. 2013) and species synchrony (Loreau and {{de
Mazancourt}} 2008) to generate predictions of community-wide species
synchrony under two limiting cases. We then confront our theoretical
predictions with simulations from the empirically-based population
models. Second, we use the multi-species population models to perform
simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific interactions
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine synchrony
\textcolor{blue}{of dominant species} in our focal grassland
communities.

\section{Theoretical Model}\subsection{The model}

While existing theory has identified
\textcolor{blue}{environmental responses, species interactions, and demographic stochasticity as the drivers of the temporal synchrony,}
we do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Appendix S1, and show that they
lead to the same overall conclusions as synchrony of per capita growth
rates.

Following Loreau and {{de Mazancourt}} (2008) and {{de Mazancourt}} et
al. (2013), we define population growth, ignoring observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the
\textcolor{blue}{temporal variance of species \emph{i}'s response to the environment and $u_{ei}(t)$ is a normal variable with unit variance that is independent among species but may be correlated.}
\textcolor{blue}{The product, $\sigma_{ei}u_{ei}(t)$, is species \emph{i}'s environmental response.}
Demographic stochasticity arises from variations in births and deaths
among individuals (e.g., same states, different fates), and is included
in the model as a first-order, normal approximation (Lande et al. 2003,
{{de Mazancourt}} et al. 2013). \(\sigma_{di}^2\) is the demographic
variance
(\textcolor{blue}{i.e., the intrinsic demographic stochasticity of species \emph{i}})
and \(u_{di}(t)\) are independent normal variables with zero mean and
unit variance
\textcolor{blue}{that allow demographic stochasiticity to vary through time.}

To derive analytical predictions we solved a first-order approximation
of Equation 2 ({{de Mazancourt}} et al. 2013 and Appendix S1). Due to
the linear approximation approach, our analytical predictions will
likely fail in communities where species exhibit large fluctuations due
to limit cycles and chaos (Loreau and {{de Mazancourt}} 2008). Indeed,
one of the advantages of focusing on growth rates rather than abundances
is that growth rates are more likely to be well-regulated around an
equilibrium value, if the long-term average of a species' growth rate is
relatively small (e.g., \(r < 2\)).

\subsection{Predictions}

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}.

Confronting our theoretical predictions with data requires estimates of
species dynamics of large populations (no demographic stochasticity)
growing in isolation (no interspecific interactions) to calculate the
covariance of species' environmental responses. To estimate
environmental responses in natural communities, we turn to our
population models built using long-term demographic data.

\section{Empirical Analysis}\subsection{Materials and methods}

\paragraph{Data.--}\label{data.}

@@

\paragraph{Calculating observed
synchrony.--}\label{calculating-observed-synchrony.}

@@

\noindent where \(\sigma_{r_{i}}\) is the temporal
\textcolor{blue}{standard deviation} of species \emph{i'}s per capita
population growth rate (\(r_i\)) and \(\sigma^{2}_{T}\) is the temporal
variance of the aggregate community-level growth rate. \(\phi\) ranges
from 0 at perfect asynchrony to 1 at perfect synchrony (Loreau and {{de
Mazancourt}} 2008). We use the same equation to calculate observed
synchrony of species' percent cover, which we present to relate our
results to previous findings, even though we focus on synchrony of
growth rates in our model simulations (see below).

\paragraph{Fitting statistical
models.--}\label{fitting-statistical-models.}

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Appendix S1 for full
details). We modeled survival probability of each genet as function of
genet size, temporal variation among years, permanent spatial variation
among groups of quadrats, and local neighborhood crowding from
conspecific and heterospecific genets. Regression coefficients for the
effect of crowding by each species can be considered a matrix of
interaction coefficients whose diagonals represent intraspecific
interactions and whose off-diagonals represent interspecific
interactions (Adler et al. 2010). These interaction coefficients can
take positive (facilitative) or negative (competitive) values. We
modeled growth as the change in size of a genet from one year to the
next, which depends on the same factors as the survival model. We fit
the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Spatial (quadrat groupings) variation was treated as a random
effect on the intercept and temporal (interannual) variation was treated
as random effects on the intercept and the effect of genet size in the
previous year (Appendix S1).

\textcolor{blue}{Interspecific and intraspecific crowding, which represent species interactions, can be included as fixed effects or as random effects that vary each year.
Strong year-to-year variation in these crowding effects would indicate a statistical interaction between environmental conditions and species interactions.
We tested for such a dynamic by comparing models with and without random year effects on crowding.
Based on the results, we decided to treat crowding as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including interannual variation in crowding did not change our results.}

@@

\paragraph{Building dynamic multi-species
models.--}\label{building-dynamic-multi-species-models.}

Once we have fit the vital rate statistical models, building the
population models is straightforward. For the IBM, we initialize the
model by randomly assigning plants spatial coordinates, sizes, and
species identities until each species achieves a density representative
of that observed in the data. We then project the model forward by using
the survival regression to determine whether a genet lives or dies, the
growth regression to calculate changes in genet size, and the
recruitment regression to add new individuals that are distributed
randomly in space. Crowding is directly calculated at each time step
since each genet is spatially referenced. Environmental stochasticity is
not an inherent feature of IBMs, but is easily included since we fit
year-specific temporal random effects for each vital rate regression. To
include temporal environmental variation, at each time step we randomly
choose a set of estimated survival, growth, and recruitment parameters
specific to one observation year. For all simulations, we ignore the
spatial random effect associated with variation among quadrat groups, so
our simulations represent an average quadrat for each site.

The IPM uses the same vital rate regressions as the IBM, but it is
spatially implicit and does not include demographic stochasticity.
Following Chu and Adler (2015), we use a mean field approximation that
captures the essential features of spatial patterning to define the
crowding index at each time step (Supporting Online Information).
Temporal variation is included in exactly the same way as for the IBM.
For full details on the IPMs we use, see Chu and Adler (2015).

\paragraph{Simulation experiments.--}\label{simulation-experiments.}

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific interactions)
were removed one-by-one and in combination. To remove interspecific
interactions, we set the off-diagonals of the interaction matrix for
each vital rate regression to zero. This retains intraspecific
interactions, and thus density-dependence, and results in simulations
where species are growing in isolation. We cannot definitively rule out
the effects of species interactions on all parameters, meaning that a
true monoculture could behave differently than our simulations of a
population growing without interspecific competitors. To remove the
effect of a fluctuating environment, we removed the temporal
(interannual) random effects from the regression equations. To remove
the effect of demographic stochasticity, we use the IPM rather than the
IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Results from an IBM with infinite population size would
converge on results from the IPM. Given computational constraints, the
largest landscape we simulate is a 25 \(\text{m}^2\) plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
interspecific interactions) present; (2) IPM: Demographic stochasticity
removed; (3) IBM: Environmental stochasticity removed; (4) IBM:
Interspecific interactions removed; (5) IPM: Interspecific interactions
and demographic stochasticity removed; (6) IBM: Interspecific
interactions and environmental stochasticity removed.
\textcolor{blue}{We did not include a simulation with only interspecific interactions because our population models run to deterministic equilibriums in the absence of environmental or demographic stochasticity.}
We ran IPM simulations for 2,000 time steps, after an initial 500
iteration burn-in period. This allowed species to reach their stable
size distribution. We then calculated yearly per capita growth rates
from the simlated time series, and then caluclated the synchrony of
species' per capita growth rates over 100 randomly selected contiguous
50 time-step sections.

We ran IBM simulations for 100 time steps, and repeated the simulations
100 times for each simulation experiment. From those, we retained only
the simulations in which no species went extinct due to demographic
stochasticity. Synchrony of per capita growth rates was calculated over
the 100 time steps for each no extinction run within a model experiment.
\textcolor{blue}{In the IBM simulations, the strength of demographic stochasticity should weaken as population size increases, meaning that synchrony should be less influenced by demographic stochasticity in large populations compared to small populations.
To explore this effect}, we ran simulations \textcolor{blue}{(4)} and
(6) on plot sizes of 1, 4, 9, 16, and 25 \(\text{m}^2\). All other IBM
simulations were run on a 25 \(\text{m}^2\) landscape
\textcolor{blue}{to most closely match the implicit, large spatial scale of the IPM simulations}.

\textcolor{blue}{Our simulations allow us to quantify the relative importance of environmental responses, species interactions, and demographic stochasticity by comparing the simulated values of community-wide species synchrony.}
The simulation experiments also allow us to test our theoretical
predictions. First, in the absence of interspecific interactions and
demographic stochasticity, populations can only fluctuate in response to
the environment. Therefore, we can use results from simulation (5) to
estimate the covariance of species' responses to the environment
(\(\text{cov}(u_{ie}, u_{je})\)) and parameterize Equation 4.
Parameterizing Equation 3 does not require simulation output because the
only parameters are the species' relative abundances. Second,
simulations (5) and (6) represent the simulated version of our limiting
case theoretical predictions.
\textcolor{blue}{This approach to testing theoretical predictions may seem circular, but recall we derived the predictions using strict assumptions about equivalence in species' growth rates, environmental response variances, and demographic variances.
Our empirically-based models do not make these assumptions.
Comparisons between parameterized predictions and simulated synchrony reveal whether the assumptions we must make to derive analytical predictions hold in the natural community our model represents.}

\subsection{Results}
